Optimal (Multiway) Spatial Joins

### 2024-05-22 msj.tex
yufei

This section will define some notions useful for our discussion. Then, we will introduce four computational geometry problems, whose solutions will serve as building bricks for our $k$-SJ algorithm.

>>>>

This section will first define some notions useful for our discussion and then introduce four computational geometry problems, whose solutions will serve as building bricks for our $k$-SJ algorithm.
